% I could not find any laws stating that in a forestry 
% (skógrækt), stating that there must be surveillance
% of the species present. (https://www.althingi.is/lagas/149a/1955003.html)

% I also checked the national park laws, and found that there
% is no such law for national parks. 
% https://www.althingi.is/lagas/149a/2004047.html #Thingvellir
% https://www.althingi.is/lagas/149a/2007060.html #Vatnajokull.

\section{Introduction}

    Currently, to gain a sense of the species of birds
    present in an area, a specialist must be sent on-site
    to observe the birds.
    
    We propose to solve this problem using cutting edge IoT
    technology, machine learning, 
    % marketing,
    and top-notch engineering. 

\section{Methods}
    We would place a number of low-power connected devices 
    in the area where we wish to observe the bird behavior.

    These devices would optimally monitor bird-song, use
    machine learning to identify which species of bird produced
    the song\cite{614790}, and using NarrowBand-IoT
    \cite{ratasuk2016overview}, a low-power communications 
    technology, report the findings to a centralized location.
     
    \subsection{Example Device}

    Since we need a relatively powerful device for the signal
    processing, an 
    acceptable choice would be the Raspberry pi, 
    (\href{https://www.raspberrypi.org/}{www.raspberrypi.org/}),
    using a NB-IoT shield 
    (\href{https://www.seeedstudio.com/Dragino-NB-IoT-Shield-B5-p-3082.html}{Dragino NB IoT Shield}
    ,
    \href{https://sixfab.com/product/raspberry-pi-nb-iot-shield/}{Sixfab NB-IoT shield}
    or
    \href{https://eu.mouser.com/ProductDetail/DFRobot/DFR0505?qs=sGAEpiMZZMve4%2FbfQkoj%252BBXWRlp4a5ROxBo2Cyn%252BqlY%3D}{Similar shield from mouser}
    )

    These parts can be rather expensive, but it is 
    likely that Siminn can supply us with some shields. 

    % To monitor the bird life, 
    We will also need a microphone to monitor the bird song.
    Which micorphone is sufficiently sensitive enough
    to capture the frequencies we are interested in is
    worth some looking into. 
    (
        \href{https://www.adafruit.com/product/1064}{Adafruit 20Hz - 20KHz mic}, 
        or
        \href{https://www.adafruit.com/product/3421}{Adafruit 50Hz - 15KHz mic}
    )

    To power our devices, a battery is needed.
    % I don't really know how hard/easy it is to get 
    % batteries into iceland.
    An example shield 
    (
        \href{https://sixfab.com/product/raspberry-pi-nb-iot-shield/}{Sixfab NB-IoT shield}
    ) 
    typically consume about 220mA while transmitting 
    at its full power, and 2mA while idling.

    The Raspberry Pi 3 B+ will at 400\% load stress consume 
    about 980 mA.

    I leave the microphone out of this count-up, since it does
    not consume a lot of power. 

    To power the raspberry, we need battery that can 
    output 5V.

    

\section{Expected value}
    We forsee that this project can become a multidisciplinary
    cooperation between the computer-science deparment and the 
    engineering department. % and maybe the business students... 

    We estimate that given enough development the outcome of 
    this project will be a marketable product for forest-keepers
    anywhere.